What We Eval in the Shadows

### 2021-08-06 paper/main.tex
Classification of the provenances

 Table~\ref{tab:detailed_provenances} shows the first provenances in number of sites, for a 85\% cumulative percentage. We only track the provenance of language expressions, not of floating point or strings for instance. In that case, the provenance is shown as \c{NA}.

\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
		Provenance & \#sites & \%sites \\
		\hline
		\packageProvenanceNamea & \packageNbProvenanceSitesa & \packagePercentProvenanceSitesa \\
		\packageProvenanceNameb & \packageNbProvenanceSitesb & \packagePercentProvenanceSitesb \\
		\packageProvenanceNamec & \packageNbProvenanceSitesc & \packagePercentProvenanceSitesc \\
		\packageProvenanceNamed & \packageNbProvenanceSitesd & \packagePercentProvenanceSitesd \\
		\packageProvenanceNamee & \packageNbProvenanceSitese & \packagePercentProvenanceSitese \\
		\packageProvenanceNamef & \packageNbProvenanceSitesf & \packagePercentProvenanceSitesf \\
		\packageProvenanceNameg & \packageNbProvenanceSitesg & \packagePercentProvenanceSitesg \\
		\packageProvenanceNameh & \packageNbProvenanceSitesh & \packagePercentProvenanceSitesh \\
		\packageProvenanceNamei & \packageNbProvenanceSitesi & \packagePercentProvenanceSitesi \\
		\packageProvenanceNamej & \packageNbProvenanceSitesj & \packagePercentProvenanceSitesj \\
		\packageProvenanceNamek & \packageNbProvenanceSitesk & \packagePercentProvenanceSitesk \\
		\packageProvenanceNamel & \packageNbProvenanceSitesl & \packagePercentProvenanceSitesl \\
		\packageProvenanceNamem & \packageNbProvenanceSitesm & \packagePercentProvenanceSitesm \\
		\packageProvenanceNamen & \packageNbProvenanceSitesn & \packagePercentProvenanceSitesn \\
		\hline
	\end{tabular}
	\caption{First provenances in number of sites.} \label{tab:detailed_provenances}
\end{table}

 We
classify them into three categories:

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions. Function arguments are
  passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\end{compactitem}

>>>>

 Table~\ref{tab:detailed_provenances} shows the first provenances in number of sites, for a 85\% cumulative percentage. We only track the provenance of language expressions, not of floating point or strings for instance. In that case, the provenance is shown as \c{NA}. We were also not able to track the provenances of some expressions in some list or data frames. In that case, the provenance that we show corresponds to the extraction step from the list, \ie \c{[[} or \c{\$}.

\begin{wraptable}{r}{5cm}\small\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Provenance & \#sites & \%sites \\
		\hline
		\packageProvenanceNamea & \packageNbProvenanceSitesa & \packagePercentProvenanceSitesa \\
		\packageProvenanceNameb & \packageNbProvenanceSitesb & \packagePercentProvenanceSitesb \\
		\packageProvenanceNamec & \packageNbProvenanceSitesc & \packagePercentProvenanceSitesc \\
		\packageProvenanceNamed & \packageNbProvenanceSitesd & \packagePercentProvenanceSitesd \\
		\packageProvenanceNamee & \packageNbProvenanceSitese & \packagePercentProvenanceSitese \\
		\packageProvenanceNamef & \packageNbProvenanceSitesf & \packagePercentProvenanceSitesf \\
		\packageProvenanceNameg & \packageNbProvenanceSitesg & \packagePercentProvenanceSitesg \\
		\packageProvenanceNameh & \packageNbProvenanceSitesh & \packagePercentProvenanceSitesh \\
		\packageProvenanceNamei & \packageNbProvenanceSitesi & \packagePercentProvenanceSitesi \\
		\packageProvenanceNamej & \packageNbProvenanceSitesj & \packagePercentProvenanceSitesj \\
		\packageProvenanceNamek & \packageNbProvenanceSitesk & \packagePercentProvenanceSitesk \\
		\packageProvenanceNamel & \packageNbProvenanceSitesl & \packagePercentProvenanceSitesl \\
		\packageProvenanceNamem & \packageNbProvenanceSitesm & \packagePercentProvenanceSitesm \\
		\packageProvenanceNamen & \packageNbProvenanceSitesn & \packagePercentProvenanceSitesn \\
		\hline
	\end{tabular}
	\caption{Provenances in number of sites (85\% first sites).} \label{tab:detailed_provenances}
\end{wraptable}

\ \NOTE{I only see 70 sites with formulas (using the class of the expression) so it does not appear here.}

 We classify them into four categories:

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions, or by building a call with \c{call} or \c{as.call}.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function. Function arguments are passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise. \c{formals} access the argument list of a function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\item {\it Symbols: }   a symbol is created with \c{as.name} or \c{as.symbol}, typically to find the value of a symbol in a non-local environment.
\end{compactitem}
